Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-04 analysis/paper/Rmd/hotspots-paper.Rmd
fixed chunk name by removing underscores

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 3, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
  bookdown::html_document2: 
    code_folding: hide
    self_contained: no
---

@@

```{r presetup}
eval_code <- TRUE
knitr::opts_chunk$set(comment=NA, fig.width=6, fig.height=6, eval = eval_code, results = "hide")
```

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 3, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::html_document2: 
    code_folding: hide
    self_contained: no
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
---

@@

```{r presetup}
eval_code <- TRUE
knitr::opts_chunk$set(comment=NA, fig.width=6, fig.height=6, eval = eval_code)
```
